Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2022-03-18 02_paper/02_study/paper_methods.Rmd
update R method

@@

# prepare data (selected from questionnaire data)
demo.data <- read_excel ("./data/data_empschul_labor_lehrperson.xlsx")

# select relevant columns
demo.data <- demo.data %>% select(LI02_01_1,
                                  LI03_01,
                                  LI04_01,
                                  LI06_05,
                                  LI10_05,
                                  LI11_01,
                                  LI13_01,
                                  LI14
                                  )

@@

demo.data$`Extracurricular Teaching Experience` <- as.numeric(demo.data$`Extracurricular Teaching Experience`)

@@

Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras (https://gopro.com/content/dam/help/hero7-black/manuals/HERO7Black_UM_ENG_REVC.pdf) from different angles.

The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.

>>>>

quest.data <- read_excel ("./data/data_empschul_labor_lehrperson.xlsx")

@@

# select relevant columns from first questionnaire 
demo.data <- quest.data %>% select(LI02_01_1,
                                  LI03_01,
                                  LI04_01,
                                  LI06_05,
                                  LI10_05,
                                  LI11_01,
                                  LI13_01,
                                  LI14
                                  )

@@

# changing character Extra. Exp. into numeric
demo.data$`Extracurricular Teaching Experience` <- as.numeric(demo.data$`Extracurricular Teaching Experience`)

@@

Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras (https://gopro.com/content/dam/help/hero7-black/manuals/HERO7Black_UM_ENG_REVC.pdf) from different angles. The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.

### Questionnaire

After each micro-teaching-unit, the students answered items on teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and scales on the teacher's presence behavior. In addition, participants were asked to give a self-assessment on  classroom management by completing the questionnaire after each micro-teaching-unit. The questionnaire was a 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).

```{r presence_questionnaire}

# select relevant columns
quest.data <- quest.data %>% select(LM01_01:LO01_02, LI06_05)

# rename columns
quest.data <- rename(quest.data, c("Group" = "LI06_05"))

# # define expert and novice with ifelse function
# quest.data$Group = ifelse(quest.data$Group < 200, "Novice","Expert")
